SVG: The Paper

### 2022-07-21 Analysis/index.Rmd
figure tweak
a few typos

We will use the model fit as detailed in @clarke2020compbio. For simplicity sake, we will characterise all of our estimated posterior probability densities with just the mean value. This gives us four parameters per participant: $b_S, b_A, b_P, b_D$.

Using these fitted values, we can now step through each target selection in the dataset and computer the probability weights our model assigns to each remaining target. For each target selection, we record:

@@

```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is. Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model. The lines give posterior samples from each indivdiaul observer."}
timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
  add_epred_draws(m, re_formula = NA, ndraws = 100) %>%
  ggplot(aes(time_taken_s, fill = condition)) + 
  stat_lineribbon(aes(y = .epred), alpha = 0.5, .width = c(0.53, 0.97)) +
  geom_jitter(data = timedat, aes(y = acc, colour = condition), 
              alpha = 0.05, width = 0, height = 0.005, colour = "black") +
  scale_x_continuous("scaled log response time (log seconds)") + 
  scale_y_continuous("model accuracy")  + 
  scale_colour_discrete(guide = "none") +
  coord_cartesian(ylim = c(0.4, 0.9)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  facet_wrap(~ condition) -> plt

@@

We can see that for these highly predictable trials, we make very few mistakes, and those that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.

@@

```{r fig.height=3, fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction. (*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length. Xs mark the outlier participants discussed above."}
path_lengths %>% filter(type == "difference") %>%
  mutate(shorter = path_length < 0) %>%
  group_by(observer, condition) %>%
  summarise(prop_shorter = mean(shorter), .groups = "drop") -> path_lengths_obs

@@

```{r}
ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 4)
```

>>>>

We will use the model fit as detailed in @clarke2020compbio. For simplicity's sake, we will characterise all of our estimated posterior probability densities with just the mean value. This gives us four parameters per participant: $b_S, b_A, b_P, b_D$.

Using these fitted values, we can now step through each target selection in the dataset and compute the probability weights our model assigns to each remaining target. For each target selection, we record:

@@

```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is. Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model. The lines give posterior samples from each individual observer."}
timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
  add_epred_draws(m, re_formula = NA, ndraws = 100) %>%
  ggplot(aes(time_taken_s, fill = condition)) + 
  stat_lineribbon(aes(y = .epred), alpha = 0.5, .width = c(0.53, 0.97)) +
  geom_jitter(data = timedat, aes(y = acc, colour = condition), 
              alpha = 0.05, width = 0, height = 0.005, colour = "black") +
  scale_x_continuous("scaled log response time (log seconds)") + 
  scale_y_continuous("model accuracy")  + 
  scale_colour_discrete(guide = "none") +
  coord_cartesian(ylim = c(0.4, 0.9)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  facet_wrap(~ condition) -> plt

@@

We can see that for these highly predictable trials, we make very few mistakes, and those mistakes that we do make appear to be related to some sort of shortest-path optimization on the part of the participant.

@@

```{r fig.height=3, fig.cap = "(*left*) A histogram showing the proportion of trials on which each participant managed a shorter path through the targets than the model's prediction. (*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length. Xs mark the outlier participants discussed above."}
path_lengths %>% filter(type == "difference") %>%
  mutate(shorter = path_length < 0) %>%
  group_by(observer, condition) %>%
  summarise(prop_shorter = mean(shorter), .groups = "drop") -> path_lengths_obs

@@

```{r}
ggsave("../Figures/path_length.pdf", plt2 + plt2b, width = 8, height = 3)
```
